### 2013-07-05 tests_test.Rmd
added follow.fitness()

plot(lambda.values, best.errors, type="l")
##############################################

# print(xtable(res.df), include.rownames = FALSE, floating = FALSE, type = "latex")
```

>>>>

plot(lambda.values, best.errors, type="l")
##############################################
# Check fitness progress

source("gapolyfuncs.R")
follow.fitness(my.data,population=200,iterations=50)

# output:

progress <- c(78.3925,78.3925,71.30467,71.30467,60.09713,20.41959,15.00416,15.00416,15.00416,15.00416,15.00416,15.00416,12.31946,12.31946,12.31946,12.31946,2.971683,2.971683,2.971683,2.971683,6.569273e-14,6.569273e-14,6.500183e-14,6.500183e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14,3.573077e-14)

df <- data.frame(iteration = 1:length(progress),
                 fitness = as.numeric(progress))

qplot(iteration, fitness, data=df) +
  geom_line() +
  ylim(0, max(df$fitness)) +
  ggtitle("Artificial dataset (population 200)")

##############################################
# print(xtable(res.df), include.rownames = FALSE, floating = FALSE, type = "latex")
```
